\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
edits and replies to comments

An inheritance data\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.} 
will be annotated with the type for the input family
and output family. There are three kinds of inheritance---extend,
override, and inherit. Extending corresponds to adding new fields,
overriding corresponds to modifying existent fields, and inheriting
corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather
than a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.

@@

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{(f : nat → nat; p : monotonic f)}\YZ{Is this semicolon syntax valid Coq syntax?} because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the family/compiled module type\YZ{I don't understand "specify the family/compiled module type"}, and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply make
\mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an
\textit{overridable} family, but "f" to be non-overridable and
transparent on its definition, and thus we can prove "p". Once we want
to swap the implementation of "f", we just override the whole ``sealed''
family.

``Sealed'' families actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

>>>>

An inheritance data\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.}\YZreply{I think this is the place where you can use an example to demonstrate these three kinds of inheritance.}
will be annotated with the type for the input family
and output family. There are three kinds of inheritance---extend,
override, and inherit. Extending corresponds to adding new fields,
overriding corresponds to modifying existent fields, and inheriting
corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather
than a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.

@@

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases where overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f},
because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the compiled module type of a given family,\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}\YZreply{Still cannot see what is going on and how it is related to the sentence that follows. An example is due.}
and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family.

``Sealed'' families can actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}\EDJreply{You are absolutely right. I should add a "can" here. I can use sealed family to simulate interface is by creating a sigma type, but making the implemntation of sigma type trivial (using place holder/using axiom as I specified below). Then once I want to instantiate with real implementation, I override the whole family -- as long as it has the same type as the sealed family, everything still works.}\YZreply{Can you explain this with an example? I recall the AbsInt example uses it?}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}\EDJreply{It really means ``place holder'' in general programming language (Python's NonImplement()), defer to future. Because Coq's Axiom can be used to instantiate anything.}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property
